2H qSIP Calculations

### 2022-03-15 qSIP_calculations_error_prop.Rmd
Create qSIP_calculations_error_prop.Rmd

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )
```

@@

>>>>

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    #a_se = ???
    #f_t_se = ???
    #f_l_se = ???
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    #u_d_se = # pull from wikipedia equation --> describe
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )
```

@@

## Error propagation

### Define a function to iterate across assimilation efficiency values
```{r}
generate_assim_error_prop <- 
  function(df_init, a_list = seq(from = 0.35, to = 0.8, by = 0.05)) {

    gen_calc_temp <- df_init

    for (k in a_list) {
      gen_calc_temp <- gen_calc_temp %>% 
      mutate(a = k) %>% 
      bind_rows(gen_calc_temp)
    }

    return(gen_calc_temp)
  }

gen_calc_errorprop <- peaks_mapped_with_zeros_analytes %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
  ) %>% 
  select(file_id,
         compound,
         sample_id,
         inc_time_d_str,
         f_label,
         t0,
         f_start,
         d_t,
         f_t,
         terrain) %>% 
  generate_assim_error_prop() %>% 
  mutate(
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                    FT = f_t, # 2F at time t (at%)
                    F0 = f_start, # 2F at t0 (at%)
                    FL = f_label, # 2F of label (at%)
                    t = d_t), # change in time (d)
      # "negative" turnovers are artifacts of noise and should be zero
      u_d = if_else(u_d < 0, 0, u_d),
      # calculate generation time, converting negatives to zero
      gen_d = if_else(u_d < 0, 0, log(2) / u_d),
    ) %>%
    mutate(
      chain_fctr = compound %>% 
        str_remove("\\d+-OH") %>% 
        parse_number() %>% 
        abs() %>% 
        {paste0("C", .)} %>% 
        factor()
        ) %>% 
    mutate(
      chain_num = compound %>% 
        str_remove("\\d+-OH") %>% 
        parse_number() %>% 
        abs()
    )

write_csv(gen_calc_errorprop, file = "data_output/gen_calc_errorprop.csv")
